---
title: "Crypto mix for investment Portfolio - Project Milestone"
author: "Sarika Singhal"
date: "July 31st 2021"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


```


# Introduction

Initial appearance of Cryptocurrency/Bitcoin/altcoin happened in 2009.Now we know it’s going to stay. Question being addressed is what is the right percentage of crypto should be in one’s investment portfolio. 

# Research Question

1. What are top cryptocurrency to be invested in and why? 
2. What mix of cryptocurrency in portfolio is best? To determine risky vs safe
3. Compare investment in crypto vs Gold & real-estate
4. How much can cryptocurrency appreciate?
5. Will cryptocurrency be used in commodity transactions soon?

# Approach

1. Identify Crypto use case and market valuation of use case vs adoption.
2. Institutional adoption 
3. World-wide laws in favor/against Cryptocurrency use.
4. Gold and Real Estate market prediction and additional costs 
5. Market volume and users for different cryptocurrency
6. Identify Age Wise risky(aggressive) investment percentage in portfolio

# How approach addresses the problem

* Future Appreciation:
  + Market valuation of use case vs current adoption can determine future growth potential
  + Gold and Real Estate appreciation prediction will provide comparison to  
* Risk factor:
  + Institutional adoption data will provide stability data around cryptocurrency to under 
  + Regional favored laws for cryptocurrency
* Market capture:
  + User and market volume provide indicators for future stability
* Investment Portfolio Mix:
  + This will provide the minimum investment strategy in cryptocurrency 
  
# Data

1.Market capitalization data for top Crypto

2.Institutional investment data in top Crypto 

3.User base of Crypto 

4.Agewise investment mix

5.Future projects for cryptocurrency 

# Required Packages

* Treemap
* Dplyr
* Tidyr
* Shiny
* Caret
* E1071
* Plotly
* tidyquant

# Plots and Table Needs

Treemap for Market capitalization
Barcharts for Risk-factor pointing of top crypto
Pie charts for crypto mix in portfolio 
Table for data staging, processing and analysis

# Next Steps

* Get the dataset for all attributes
* Transform the data for processing
* Analyze the data 
* Setting up correlation between different data.
* Data visualization




```{r cars}


```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## References
install.packages("knitr")

